---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

All commands that you use to use when developing packages...

# First time just after creating the project

- Fill the following chunk to create the DESCRIPTION of your package

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(overwrite = F,
  pkg = here::here(),
  fields = list(
    Title = "A package with new functions to run EQM algorithm",
    Description = "Here I will test fucntions to run the eqm algorithm before I pass them to {histoc}",
    `Authors@R` = c(
      person("Lima", "Bruno", email = "balima78@gmail.com", role = c("aut", "cre"), comment = c(ORCID = "0000-0001-9090-4457")),
      person(given = "TxOR", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("")
```

# Start using git

```{r, eval=FALSE}
usethis::use_git()
# Deal with classical files to ignore
usethis::git_vaccinate()
# Use main for primary branch
usethis::git_default_branch_rename()
```

# Set extra sources of documentation

```{r, eval=FALSE}
# Install a first time
remotes::install_local()
# README
usethis::use_readme_rmd()
# Code of Conduct
usethis::use_code_of_conduct("balima78@gmail.com")
# NEWS
usethis::use_news_md()
```

# Including datasets

to include datasets we need the package to already be built; only once the package exists can we include data sets. 

```{r}
#library(simK)
local({
  cds <- simK::candidates_df(n = 2000, prob.urgent = 0) |>
    dplyr::select(ID, bg, A1, A2, B1, B2, DR1, DR2, age, dialysis, cPRA, urgent)
#dns <- simK::donors_df(n = 280)
#ant <-  simK::Abs_df(candidates =cds)
  
  usethis::use_data(cds, overwrite = TRUE)
  # usethis::use_data(dns, overwrite = TRUE)
  #usethis::use_data(ant, overwrite = TRUE)
})

```

**From now, you will need to "inflate" your package at least once to be able to use the following commands. Let's go to your flat template, and come back here later if/when needed.**


# Package development tools
## Use once

```{r, eval=FALSE}
# Pipe
usethis::use_pipe()

# package-level documentation
usethis::use_package_doc()

# GitHub
# Add your credentials for GitHub
gitcreds::gitcreds_set()
# Send your project to a new GitHub project
usethis::use_github()

# Set Continuous Integration
# _GitHub
usethis::use_github_action_check_standard()
usethis::use_github_action("pkgdown")
usethis::use_github_action("test-coverage")
# _GitLab
gitlabr::use_gitlab_ci(type = "check-coverage-pkgdown")

# Add new flat template
fusen::add_flat_template("add")
```

## Use everytime needed

```{r}
# Simulate package installation
pkgload::load_all()

# Generate documentation and deal with dependencies
attachment::att_amend_desc()

# Check the package
devtools::check()
```

# Share the package

```{r}
# set and try pkgdown documentation website
usethis::use_pkgdown()
pkgdown::build_site()

# build the tar.gz with vignettes to share with others
devtools::build(vignettes = TRUE)
```

